Efficient Thresholded Correlation using Truncated Singular Value Decomposition

### 2015-12-20 threshold/draft.Rnw
Addresses

\Abstract{
Efficiently computing a subset of a correlation matrix consisting of values
above a specified threshold is important to many practical applications.
Real-world problems in genomics, machine learning, finance other applications
can produce correlation matrices too large to explicitly form and tractably
compute. Often, only values corresponding to highly-correlated vectors are of
interest, and those values typically make up a small fraction of the overall
correlation matrix. We present a method based on the singular value
decomposition (SVD) and its relationship to the data covariance structure that
can efficiently compute thresholded subsets of very large correlation matrices.
}
\Keywords{thresholded correlation, SVD, \proglang{R}}
\Plainkeywords{thresholded correlation, SVD, R}
\Address{
James Baglama, Chair of Mathematics\\
Department of Mathematics\\
University of Rhode Island\\
Kingston, Rhode Island 02881\\
E-mail: \email{jbaglama@math.uri.edu}\\
URL: \url{http://www.math.uri.edu/~jbaglama}\\
}

>>>>

\Abstract{
Efficiently computing a subset of a correlation matrix consisting of values
above a specified threshold is important to many practical applications.
Real-world problems in genomics, machine learning, finance other applications
can produce correlation matrices too large to explicitly form and tractably
compute. Often, only values corresponding to highly-correlated vectors are of
interest, and those values typically make up a small fraction of the overall
correlation matrix. We present a method based on the singular value
decomposition (SVD) and its relationship to the data covariance structure that
can efficiently compute thresholded subsets of very large correlation matrices.
}
\Keywords{thresholded correlation, SVD, \proglang{R}}
\Plainkeywords{thresholded correlation, SVD, R}
\Address{
James Baglama, Chair of Mathematics\\
Department of Mathematics\\
University of Rhode Island\\
Kingston, Rhode Island 02881\\
E-mail: \email{jbaglama@math.uri.edu}\\
URL: \url{http://www.math.uri.edu/~jbaglama}\\
\\
Michael Kane\\
Yale University\\
300 Geroge Street\\
New Haven, Connecticut 06511\\
E-mail: \email{michael.kane@yale.edu}\\
\\
Bryan Lewis\\
Paradigm4, Inc.\\
281 Winter Street, Suite 360\\
Waltham, MA 02451\\
E-mail: \email{blewis@illposed.net}\\
URL: \url{http://illposed.net}\\
\\
Alex Poliakov\\
Paradigm4, Inc.\\
281 Winter Street, Suite 360\\
Waltham, MA 02451\\
E-mail: \email{apoliakov@paradigm4.com}\\
}
